Atlantis to SS for California Current sardines and hake: full fishing and climate scenario

### 2019-07-08 SardinesHakeatlantisom2SStest.Rmd
testing sardine and hake with new CC run

---
title: "Sardines only end-to-end atlantisom test"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

Now we test the `atlantisom` to SS workflow with a new California Current run that includes climate forcing, recruitment variability, and the fishing scenario outlined for our project in Norway: "output_CC_2063_run11".

@@

species_ss <- c("Pacific_sardine")

@@

if(initCCA) source(here("config/CC2Config.R"))

@@

```{r trueB-N, eval=FALSE}

@@

```{r true-comps, warning=FALSE, message=FALSE, eval=FALSE}

@@

# save age comps
saveRDS(numssshigh, file.path(d.name, paste0(scenario.name, "natage_census_sard.rds")))

@@

#save for later use, takes a long time to generate
saveRDS(length_census_ss, file.path(d.name, paste0(scenario.name, "lengthwt_census_sard.rds")))

@@

Natage <- readRDS(file.path(d.name, paste0(scenario.name, "natage_census_sard.rds")))

@@

lengthwt_census_ss <- readRDS(file.path(d.name, paste0(scenario.name, "lengthwt_census_sard.rds")))

@@

# save true total catch in numbers by timestep, need to sum to year
saveRDS(totcatchN, file.path(d.name, paste0(scenario.name, "catchN_census_sard.rds")))

@@

# save true catch at age
saveRDS(catch_numssshigh, file.path(d.name, paste0(scenario.name, "catchage_census_sard.rds")))

@@

#save for later use, takes a long time to generate
saveRDS(catch_length_census_ss, file.path(d.name, paste0(scenario.name, "catchlengthwt_census_sard.rds")))

@@

catch_numssshigh <- readRDS(file.path(d.name, paste0(scenario.name, "catchage_census_sard.rds")))

@@

totcatchN <- readRDS(file.path(d.name, paste0(scenario.name, "catchN_census_sard.rds")))

@@

catch_numssshigh <- readRDS(file.path(d.name, paste0(scenario.name, "catchage_census_sard.rds")))

catch_lengthwt_census_ss <- readRDS(file.path(d.name, paste0(scenario.name, "catchlengthwt_census_sard.rds")))

>>>>

---
title: "Atlantis to SS for California Current sardines and hake: full fishing and climate scenario"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

Now we test the `atlantisom` to SS workflow with a new California Current run that includes climate forcing, recruitment variability, and the fishing scenario outlined for our project in Norway: "output_CC_2063_OA_OFF_222".

@@

species_ss <- c("Pacific_sardine", "Mesopel_M_Fish")

@@

if(initCCA) source(here("config/CC3Config.R"))

@@

```{r trueB-N}

@@

```{r true-comps, warning=FALSE, message=FALSE}

@@

# save age comps
saveRDS(numssshigh, file.path(d.name, paste0(scenario.name, "natage_census_sard_hake.rds")))

@@

#save for later use, takes a long time to generate
saveRDS(length_census_ss, file.path(d.name, paste0(scenario.name, "lengthwt_census_sard_hake.rds")))

@@

Natage <- readRDS(file.path(d.name, paste0(scenario.name, "natage_census_sard_hake.rds")))

@@

lengthwt_census_ss <- readRDS(file.path(d.name, paste0(scenario.name, "lengthwt_census_sard_hake.rds")))

@@

# save true total catch in numbers by timestep, need to sum to year
saveRDS(totcatchN, file.path(d.name, paste0(scenario.name, "catchN_census_sard_hake.rds")))

@@

# save true catch at age
saveRDS(catch_numssshigh, file.path(d.name, paste0(scenario.name, "catchage_census_sard_hake.rds")))

@@

#save for later use, takes a long time to generate
saveRDS(catch_length_census_ss, file.path(d.name, paste0(scenario.name, "catchlengthwt_census_sard_hake.rds")))

@@

catch_numssshigh <- readRDS(file.path(d.name, paste0(scenario.name, "catchage_census_sard_hake.rds")))

@@

totcatchN <- readRDS(file.path(d.name, paste0(scenario.name, "catchN_census_sard_hake.rds")))

@@

catch_numssshigh <- readRDS(file.path(d.name, paste0(scenario.name, "catchage_census_sard_hake.rds")))

catch_lengthwt_census_ss <- readRDS(file.path(d.name, paste0(scenario.name, "catchlengthwt_census_sard_hake.rds")))
